\documentclass[../../Aurora C# unofficial manual.tex]{subfiles}

\begin{document}
		\section{Independence}\label{6_independence}
	Original post can be found
	\href{http://aurora2.pentarch.org/index.php?topic=8495.msg118467#msg118467}{here}.
	\\\\
	In C\#, you can declare a colony independent using a button on the Economics window. Colonies may also become independent in other situations, such as a rebellion following high unrest. Independence is far more complex than it first sounds, because the population will be under the control of a new race that is essentially a copy of the original race. The process is as follows:
	\begin{itemize}
		\item The title of the new race will be based on the name of the newly-independent population.
		\item A new flag will be auto-selected and random naming themes chosen for classes, systems, etc.. Commander name themes will remain the same as the original race.
		\item The ranks of the new race will copy the ranks of the original race.
		\item Any ground forces at the population will be transferred to the new race.
		\item It is possible that an NPR population can become independent, in which cases it will retain the same tech but create a new design philosophy.
		\item The new race will start with an amount of wealth equal to \( Total Original Race Wealth * Independent Pop Size / Total Original Race Pop Size Before Independence \), which will be transferred from the original race.
		\item The new race will start with a number of commanders equal to original race number of \( Commanders * Independent Pop Size / Total Original \) race pop size before independence). These are new commanders and not transferred from the original race.
		\item A top-level admin command will be created at the population.
	\end{itemize}
	
	
	The new race will gain the following knowledge from the original race:
	\begin{itemize}
		\item The same galactic map, including map labels.
		\item All geological and gravitational survey data.
		\item All tech systems.
		\item How to build all ship components and missiles.
		\item All class designs.
		\item All ground unit class designs.
		\item All ground formation templates.
		\item All intelligence data, including alien races, classes, ships, sensors, weapons, populations and ground forces.
		\item A complete set of intelligence information on the original race which will be set up as a new alien race, with known systems, ships, etc.
		\item Control Race flags on galactic map.
		\item Protection Status settings for different combination of alien races and systems.
		\item Locations of ruins, anomalies, wrecks, etc..
		\item Event colours.
	\end{itemize}
	
	For manual independence, any naval forces will have to be transferred using the Transfer Fleet option. In the case of a rebellion, some ships may be transferred automatically.
\end{document}